Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.Rmd
clean up the background

  table_dat %>%
  knitr::kable(col.names = c("Residual plots", "Departures", "Model structural", "Breusch-Pagan", "Shapiro–Wilk"),
               align = "llrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are colored in red.', 
               label = "example-residual-plot-table" )

@@

(This sec)

@@

### p-value calculation

Further, a visual test can involve $K$ independent observers. Let $D_i = \{0,1\}$ be a binomial random variable denoting whether subject $i$ correctly detecting the actual data plot, and $X = \sum_{i=1}^{K}X_i$ be the number of observers correctly picking the actual data plot. Then, by imposing a relatively strong assumption on the visual test that all $K$ evaluations are fully independent, under the null hypothesis, $X \sim \mathrm{Binom}_{K,1/m}$. Therefore, the $p$-value of a lineup of size $m$ evaluated by $K$ observer is given as \begin{equation} \label{eq:pvaluesingle}
P(X \geq x) = \sum_{i=x}^{K}{{K}\choose{i}}\left(\frac{1}{m}\right)^i\left(\frac{m-1}{m}\right)^{k-i},
\end{equation}

where $x$ is the realization of number of observers correctly picking the actual data plot [@majumder_validation_2013].

<!-- remove the binomial one -->

As pointed out by @vanderplas2021statistical, though Equation (\ref{eq:pvaluesingle}) is trivial, but it doesn't take into account the possible dependencies in the visual test due to repeated evaluations of the same lineup. And it is inapplicable to visual test where subjects are asked to select one or more "most different" plots from the lineup. They summarized three common different scenarios in visual inference: (1) $K$ different lineups are shown to $K$ subjects, (2) $K$ lineups with different null plots but the same actual data plot are shown to $K$ subjects, and (3) the same lineup is shown to $K$ subjects. Out of these three scenarios, Scenario 3 is the most common in previous studies as it puts the least constraints on the experimental design. For Scenario 3, @vanderplas2021statistical modelled the probability of a plot $i$ being selected from a lineup as $\theta_i$, where $\theta_i \sim Dirichlet(\alpha)$ for $i=1,...,m$ and $\alpha > 0$. And defined $c_i$ to be the number of times plot $i$ being selected in $K$ evaluations. In case subject $j$ makes multiple selections, they decided to add $1/s_j$ to $c_i$ instead of one, where $s_j$ is the number of plots subject $j$ selected for $j=1,...K$. This ensured $\sum_{i}c_i=K$. Thus, the visual p-value followed by the above model is given as

@@

<!-- a sentence to discuss alpha  -->

@@

<!-- Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualization" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, in the Bayesian context, data plots was systematically considered as model diagnostics by taking advantage of the data simulated from the assumed statistical models [@gelman_bayesian_2003; @gelman_exploratory_2004]. -->

<!-- It was surprising that the essential components of visual inference had actually been established in @buja_inference_1999, but it was not until 10 years later that @buja_statistical_2009 formalized it as an inferential framework to extend confirmatory statistics to visual discoveries. This framework redefines the test statistics, tests, null distribution, significance levels and $p$-value for visual discovery modelled on the confirmatory statistical testing. Figure \ref{fig:parallelism} outlines the parallelism between conventional tests and visual discovery. -->

@@

<!-- In visual inference, a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$ is defined, where $\boldsymbol{\mathrm{y}}$ is the data and $I$ is a set of all possible visual features. @buja_statistical_2009 described each of the test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})$ as a measurement of the degree of presence of a visual feature. Alternatively, @majumder_validation_2013 avoids the use of visual features and defined the visual statistics $T(.)$ as a mapping from a dataset to a data plot. Both definitions of visual test statistics are valid, but in the rest of the paper the first definition will be used as it covers some details needed by the following discussion. A visual discovery is defined as a rejection of a null hypothesis, and the same null hypothesis can be rejected by many different visual discoveries [@buja_statistical_2009]. For regression diagnostics, the null hypothesis would be the assumed model, while the visual discoveries would be any findings that are inconsistent with the null hypothesis. The same regression model can be rejected by many reasons with residual plot, including non-linearity and heteroskedasticity as shown in Figure \ref{fig:residual-plot-cubic-heter}. -->

@@

<!-- ### Sampling from the null distribution {#se:sampling-from-null} -->

<!-- The null distribution of plots refers to the infinite collection of plots of null datasets sampled from $H_0$. It is defined as the analogue of the null distribution of test statistics in conventional test [@buja_statistical_2009]. In practice, a finite number of plots of null datasets could be generated, called null plots. In the context of regression diagnostics, sampling data from $H_0$ is equivalent to sampling data from the assumed model. As @buja_statistical_2009 suggested, $H_0$ is usually composited by a collection of distributions controlled by nuisance parameters. Since regression models can have various forms, there is no general solution to this problem, but it sometimes can be reduced to so called "reference distribution" by applying one of the three methods: (i) sampling from a conditional distribution given a minimal sufficient statistic under $H_0$, (ii) parametric bootstrap sampling with nuisance parameters estimated under $H_0$, and (iii) Bayesian posterior predictive sampling. -->

<!-- The conditional distribution given a minimal sufficient statistic is the best justified reference distribution among the three [@buja_statistical_2009]. Suppose there exists a minimal sufficient statistic $\boldsymbol{S}(\boldsymbol{y})$ under the null hypothesis, any null datasets $\boldsymbol{y^{*}}$ should fulfil the condition $\boldsymbol{S}(\boldsymbol{y}) = \boldsymbol{s}$. Using the classical normal linear regression model as example, the minimal sufficient statistic is $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{\beta}}, \boldsymbol{e}'\boldsymbol{e})$, where $\hat{\boldsymbol{\beta}}$ are the coefficient estimators and $\boldsymbol{e}'\boldsymbol{e}$ is the residual sum of square. Alternatively, the minimal sufficient statistic can be constructed as $\boldsymbol{S}(\boldsymbol{y}) = (\hat{\boldsymbol{y}}, ||\boldsymbol{e}||)$, where $\hat{\boldsymbol{y}}$ are the fitted values and $||\boldsymbol{e}||$ is the length of residuals, which is more intuitive as suggested by @buja_statistical_2009. Since the fitted values are held fixed, the variation can only occur in the residual space. And because the length of residual is also held fixed, residuals obtained from a null dataset has to be a random rotation of $\boldsymbol{e}$ in the residual space. With this property, null residuals can be simulated by regressing $N$ i.i.d standard normal random draws on the regressors, then rescaling it by the ratio of residual sum of square in two regressions. -->

<!-- ### Lineup protocol {#se:lineup} -->

<!-- With the simulation mechanism of null plots being provided, another aspect of hypothesis testing that needs to be addressed is the control of false positive rate or Type I error. Any visual statistic $T^{(i)}(\boldsymbol{\mathrm{y}})$ needs to pair with a critical value $c^{(i)}$ to form a hypothesis test. When a visual feature $i$ is discovered by the observer from a plot, the corresponding visual statistic $T^{(i)}(\boldsymbol{\mathrm{y}})$ may not be known as there is no general agreement on the measurement of the degree of presence of a visual feature. It is only the event that $T^{(i)}(\boldsymbol{\mathrm{y}}) > c^{(i)}$ is confirmed. Similarly, if any visual discovery is found by the observer, we say, there exists $i \in I:~T^{(i)}(\boldsymbol{\mathrm{y}}) > c^{(i)}$ [@buja_statistical_2009]. -->

<!-- Using the above definition, the family-wise Type I error can be controlled if one can provide the collection of critical values $c^{(i)}~(i \in I)$ such that $P(\mathrm{there~exists~} i \in I: T^{(i)}(\boldsymbol{\mathrm{y}}) > c^{(i)}|\boldsymbol{\mathrm{y}}) \leq \alpha$, where $\alpha$ is the significance level. However, since the quantity of $T^{(i)}(\boldsymbol{\mathrm{y}})$ may not be known, such collection of critical values can not be provided. -->

<!-- @buja_statistical_2009 proposed the lineup protocol as a visual test to calibrate the Type I error issue without the specification of $c^{(i)}~(i \in I)$. It is inspired by the "police lineup" or "identity parade" which is the act of asking the eyewitness to identify criminal suspect from a group of irrelevant people. The protocol consists of $m$ randomly placed plots, where one plot is the actual data plot, and the remaining $m - 1$ plots have the identical graphical production as the data plot except the data has been replaced with data consistent with the null hypothesis. Then, an observer who have not seen the actual data plot will be asked to point out the most different plot from the lineup. -->

<!-- Under the null hypothesis, it is expected that the actual data plot would have no distinguishable difference with the null plots, and the probability of the observer correctly picks the actual data plot is $1/m$. If we reject the null hypothesis as the observer correctly picks the actual data plot, then the Type I error of this test is $1/m$. -->

<!-- This provides us with an mechanism to control the Type I error, because $m$ - the number of plots in a lineup can be chosen. A larger value of $m$ will result in a smaller Type I error, but the limit to the value of $m$ depends on the number of plots a human is willing to view [@buja_statistical_2009]. Typically, $m$ will be set to $20$ which is equivalent to set $\alpha = 0.05$, a general choice of significance level for conventional testing among statisticians. -->

<!-- Further, a visual test can involve $K$ independent observers. Let $D_i = \{0,1\}$ be a binomial random variable denoting whether subject $i$ correctly detecting the actual data plot, and $X = \sum_{i=1}^{K}X_i$ be the number of observers correctly picking the actual data plot. Then, by imposing a relatively strong assumption on the visual test that all $K$ evaluations are fully independent, under the null hypothesis, $X \sim \mathrm{Binom}_{K,1/m}$. Therefore, the $p$-value of a lineup of size $m$ evaluated by $K$ observer is given as \begin{equation} \label{eq:pvaluesingle} -->
<!-- P(X \geq x) = \sum_{i=x}^{K}{{K}\choose{i}}\left(\frac{1}{m}\right)^i\left(\frac{m-1}{m}\right)^{k-i}, -->
<!-- \end{equation} -->

<!-- where $x$ is the realization of number of observers correctly picking the actual data plot [@majumder_validation_2013]. -->

<!-- The multiple individuals approach avoids the limit of $m$, while provides visual tests with $p$-value much smaller than $0.05$. In fact, the lower bound of $p$-value decreases exponentially as $K$ increases. With just $4$ individuals and $20$ data plots in a lineup, the $p$-value could be as small as $0.0001$. Additionally, by involving multiple observers, variation of individual ability to read plots can be addressed to some degree as different opinions about visual discoveries can be collected. -->

<!-- As pointed out by @vanderplas2021statistical, though Equation (\ref{eq:pvaluesingle}) is trivial, but it doesn't take into account the possible dependencies in the visual test due to repeated evaluations of the same lineup. And it is inapplicable to visual test where subjects are asked to select one or more "most different" plots from the lineup. They summarized three common different scenarios in visual inference: (1) $K$ different lineups are shown to $K$ subjects, (2) $K$ lineups with different null plots but the same actual data plot are shown to $K$ subjects, and (3) the same lineup is shown to $K$ subjects. Out of these three scenarios, Scenario 3 is the most common in previous studies as it puts the least constraints on the experimental design. For Scenario 3, @vanderplas2021statistical modelled the probability of a plot $i$ being selected from a lineup as $\theta_i$, where $\theta_i \sim Dirichlet(\alpha)$ for $i=1,...,m$ and $\alpha > 0$. And defined $c_i$ to be the number of times plot $i$ being selected in $K$ evaluations. In case subject $j$ makes multiple selections, they decided to add $1/s_j$ to $c_i$ instead of one, where $s_j$ is the number of plots subject $j$ selected for $j=1,...K$. This ensured $\sum_{i}c_i=K$. -->

<!-- The full model was a Dirichlet-multinomial mixture distribution -->

<!-- ```{=tex} -->
<!-- \begin{align} \label{eq:dirichlet-multinomial}\begin{split} -->
<!-- \boldsymbol{\theta}&|\alpha \sim Dirichlet(\alpha)\\ -->
<!-- (c_i,...,c_m)&|\boldsymbol{\theta} \sim Multinomial(K, \boldsymbol{\theta}). -->
<!-- \end{split}\end{align} -->
<!-- ``` -->
<!-- Since the p-value calculation only needs to concern the number of times the actual data plot being selected denoted by $C_i$, they showed the model can be simplified to a beta-binomial mixture distribution -->

<!-- ```{=tex} -->
<!-- \begin{align} \label{eq:beta-binomial}\begin{split} -->
<!-- \theta_i&|\alpha \sim Beta(\alpha, (m-1)\alpha)\\ -->
<!-- C_i&|\theta_i \sim Binomial(K, \theta_i). -->
<!-- \end{split}\end{align} -->
<!-- ``` -->
<!-- Thus, the visual p-value followed by the beta-binomial model is given as -->

<!-- ```{=tex} -->
<!-- \begin{equation} \label{eq:pvalue-beta-binomial} -->
<!-- P(C \geq c_i) = \sum_{x=c_i}^{K}{{K}\choose{x}}\frac{1}{B(\alpha, (m-1)\alpha)}B(x + \alpha, K - x + (m - 1)\alpha), -->
<!-- \end{equation} -->
<!-- ``` -->
<!-- where $B(.)$ is the beta function defined as -->

<!-- ```{=tex} -->
<!-- \begin{equation} \label{eq:betafunction} -->
<!-- B(a, b) = \int_{0}^{1}t^{\alpha - 1}(1-t)^{b-1}dt,\quad \text{where}\quad a,b>0.  -->
<!-- \end{equation} -->
<!-- ``` -->

<!-- Note that the use of Equation (\ref{eq:pvalue-beta-binomial}) requires the estimation of $\hat{\alpha}$, which largely depends on the null model, the type of the plot and other aesthetic features. They suggested to estimate $\hat{\alpha}$ visually based on the selections of null plots of the experimental data, or to estimate $\hat{\alpha}$ numerically based on several additional Rorschach lineups, which is a type of lineup containing only null plots. However, when the number of null models are large, it could be expensive to manually estimate each $\alpha$ or include additional Rorschach lineups in the experiment. -->

<!-- Instead, in the experiments that will be described in section \ref{experimental-design}, we adopt a simpler model implicitly used by the `pmulti()` function of the `vinference` `R` package. We assume the attractiveness of the plot $i$ modelled as $w_i \sim Uniform(0,1)$ for $i=1,..,m$. Let $\theta_i = w_i/\sum_{i=1}^{m}w_i$ be the probability of plot $i$ being selected by a subject. Then, given the number of selections $s_j$, for $j=1,...,K$, the distribution of $C_i$ can be approximated by simulating the random selection process with computer. The simulated visual test p-value is formulated as -->

<!-- ```{=tex} -->
<!-- \begin{equation} \label{eq:p-value-multi} -->
<!-- \text{p-value} = \frac{\#draws~that~the~actual~data~plota~being~selected~more~than~c_i~times}{\#simulation}. -->
<!-- \end{equation} -->
<!-- ``` -->
<!-- ### Effectiveness of visual inference in regression diagnostics -->

<!-- Compared to the conventional test, whose power only depends on the parameter of interest $\theta$, several studies [see @hofmann_graphical_2012; @majumder_validation_2013; @majumder2014human; @roy_chowdhury_using_2015; @loy2016variations] have shown the power of the visual test is subject-specific. Thus, to be able to account for individual's ability, an individual is required to evaluate multiple lineups [@majumder_validation_2013].   -->

<!-- Suppose individuals have the same ability and a lineup has been evaluated by multiple individuals, under the alternative hypothesis, the estimated power for a lineup can be expressed as $\hat{p} = x/K$, the estimated probability of identifying the actual data plot from the lineup. If the individual skill needs to be taken into account, and $L$ lineups have been evaluated by $K$ individuals, @majumder_validation_2013 suggests that mixed effects logistic regression model can be fit as: -->

<!-- $$g(p_{li}) = W_{li}\delta + Z_{li}\tau_{li},$$ -->

<!-- where $g(.)$ is the logit link function $g(p) = log(p)  - log(1-p)$; $0 \leq p \leq 1$. $W_{li}$, $1 \leq i \leq K$, $1 \leq l \leq L$, is the covariate matrix including lineup-specific elements and demographic information of individuals, and $\delta$ is a vector of parameters. $Z$ is the random effects matrix, and $\tau$ is a vector of variables follow $N(\boldsymbol{0},\sigma_{\tau}\boldsymbol{I}_{KL\times KL})$.  -->

<!-- Then, the estimated power for lineup $l$ and individual $i$ can be calculated as $\hat{p}_{li} = g^{-1}(W_{li}\hat{\delta} + Z_{li}\hat{\tau}_{li})$ [@majumder_validation_2013]. -->

## Effectiveness of visual test in regression diagnostics

The effectiveness of visual inference has already been validated by @majumder_validation_2013 under relatively simple classical normal linear regression model settings with only one or two regressors. Their results suggest visual test is capable of testing the significance of a single regressor with a similar power as a t-test, though they expressed that in general it is unnecessary to use visual inference if there exists a conventional test and they didn't expect the visual test to perform equally well as the conventional test. In their third experiment, where there does not exist a proper conventional test, visual test outperforms the conventional test for a large margin. This is encouraging as it promotes the use of visual inference in border field of data science where there are no existing statistical testing procedures. In fact, lineup protocol has been integrated into some model diagnostic tools such as @loy2013diagnostic.

<!-- refactoring from here -->

With our knowledge, what haven't been examined so far is the effectiveness of visual test relative to the equivalent conventional test in regression diagnostics. Particularly, its ability to detect non-linearity and heteroskedasticity compared to F-test and BP-test.

@@

>>>>

  table_dat %>%
  knitr::kable(col.names = c("Residual plots", "Departures", "Model structural", "Breusch-Pagan", "Shapiro–Wilk"),
               align = "llrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Example residual plots examined by the corresponding conventional tests. P-values smaller than 0.05 are showed in bold.', 
               label = "example-residual-plot-table" )

@@

(This section introduces the lineup protocol, and briefly discusses the method for sampling null data, calculating the p-value and estimating power.)

@@

### P-value calculation

Further, a visual test can involve $K$ independent observers. Let $D_i = \{0,1\}$ be a binomial random variable denoting whether subject $i$ correctly detecting the actual data plot, and $X = \sum_{i=1}^{K}X_i$ be the number of observers correctly picking the actual data plot. Then, by imposing a relatively strong assumption on the visual test that all $K$ evaluations are fully independent, under the null hypothesis, $X \sim \mathrm{Binom}_{K,1/m}$. Therefore, the $p$-value of a lineup of size $m$ evaluated by $K$ observer is given as $P(X \geq x) = 1 - F(x) + f(x)$, where $F(.)$ is the cumulative distribution function, $f(.)$ is the probability mass function and $x$ is the realization of number of observers correctly picking the actual data plot [@majumder_validation_2013].

As pointed out by @vanderplas2021statistical, the binomial model doesn't take into account the possible dependencies in the visual test due to repeated evaluations of the same lineup. And it is inapplicable to visual test where subjects are asked to select one or more "most different" plots from the lineup. They summarized three common scenarios in visual inference: (1) $K$ different lineups are shown to $K$ subjects, (2) $K$ lineups with different null plots but the same actual data plot are shown to $K$ subjects, and (3) the same lineup is shown to $K$ subjects. Out of these three scenarios, Scenario 3 is the most common in previous studies as it puts the least constraints on the experimental design. For Scenario 3, @vanderplas2021statistical modelled the probability of a plot $i$ being selected from a lineup as $\theta_i$, where $\theta_i \sim Dirichlet(\alpha)$ for $i=1,...,m$ and $\alpha > 0$. And defined $c_i$ to be the number of times plot $i$ being selected in $K$ evaluations. In case subject $j$ makes multiple selections, they decided to add $1/s_j$ to $c_i$ instead of one, where $s_j$ is the number of plots subject $j$ selected for $j=1,...K$. This ensured $\sum_{i}c_i=K$. Thus, the visual p-value followed by the above model is given as

@@

The parameter $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} is usually unknown and hence needs to be estimated from the survey data. For low values of $\alpha$, only a few plots are attractive to the observers and tend to be selected. For higher values of $\alpha$, the distribution of the probability of each plot being selected is more evenly. @vanderplas2021statistical suggested that $\alpha$ can be estimated using maximum likelihood estimation or visual estimation. But if $\alpha$ is small and only a few null plots in a lineup are attractive, MLE could fail to provide accurate estimates.

@@

@@

@@

## Unknown

This should be a section that summarizes the background, gives the motivation to the experiments, and most importantly reflects on the title.

@@

(This section discu)

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.tex
clean up the background

\hypertarget{p-value-calculation}{%
\subsubsection{p-value calculation}\label{p-value-calculation}}

Further, a visual test can involve \(K\) independent observers. Let
\(D_i = \{0,1\}\) be a binomial random variable denoting whether subject
\(i\) correctly detecting the actual data plot, and
\(X = \sum_{i=1}^{K}X_i\) be the number of observers correctly picking
the actual data plot. Then, by imposing a relatively strong assumption
on the visual test that all \(K\) evaluations are fully independent,
under the null hypothesis, \(X \sim \mathrm{Binom}_{K,1/m}\). Therefore,
the \(p\)-value of a lineup of size \(m\) evaluated by \(K\) observer is
given as \begin{equation} \label{eq:pvaluesingle}
P(X \geq x) = \sum_{i=x}^{K}{{K}\choose{i}}\left(\frac{1}{m}\right)^i\left(\frac{m-1}{m}\right)^{k-i},
\end{equation}

where \(x\) is the realization of number of observers correctly picking
the actual data plot \citep{majumder_validation_2013}.

As pointed out by \citet{vanderplas2021statistical}, though Equation
(\ref{eq:pvaluesingle}) is trivial, but it doesn't take into account the
possible dependencies in the visual test due to repeated evaluations of
the same lineup. And it is inapplicable to visual test where subjects
are asked to select one or more ``most different'' plots from the
lineup. They summarized three common different scenarios in visual
inference: (1) \(K\) different lineups are shown to \(K\) subjects, (2)
\(K\) lineups with different null plots but the same actual data plot
are shown to \(K\) subjects, and (3) the same lineup is shown to \(K\)
subjects. Out of these three scenarios, Scenario 3 is the most common in
previous studies as it puts the least constraints on the experimental
design. For Scenario 3, \citet{vanderplas2021statistical} modelled the
probability of a plot \(i\) being selected from a lineup as
\(\theta_i\), where \(\theta_i \sim Dirichlet(\alpha)\) for
\(i=1,...,m\) and \(\alpha > 0\). And defined \(c_i\) to be the number
of times plot \(i\) being selected in \(K\) evaluations. In case subject
\(j\) makes multiple selections, they decided to add \(1/s_j\) to
\(c_i\) instead of one, where \(s_j\) is the number of plots subject
\(j\) selected for \(j=1,...K\). This ensured \(\sum_{i}c_i=K\). Thus,
the visual p-value followed by the above model is given as

@@

@@

\hypertarget{effectiveness-of-visual-test-in-regression-diagnostics}{%
\subsection{Effectiveness of visual test in regression
diagnostics}\label{effectiveness-of-visual-test-in-regression-diagnostics}}

The effectiveness of visual inference has already been validated by
\citet{majumder_validation_2013} under relatively simple classical
normal linear regression model settings with only one or two regressors.
Their results suggest visual test is capable of testing the significance
of a single regressor with a similar power as a t-test, though they
expressed that in general it is unnecessary to use visual inference if
there exists a conventional test and they didn't expect the visual test
to perform equally well as the conventional test. In their third
experiment, where there does not exist a proper conventional test,
visual test outperforms the conventional test for a large margin. This
is encouraging as it promotes the use of visual inference in border
field of data science where there are no existing statistical testing
procedures. In fact, lineup protocol has been integrated into some model
diagnostic tools such as \citet{loy2013diagnostic}.

With our knowledge, what haven't been examined so far is the
effectiveness of visual test relative to the equivalent conventional
test in regression diagnostics. Particularly, its ability to detect
non-linearity and heteroskedasticity compared to F-test and BP-test.

>>>>

\hypertarget{p-value-calculation}{%
\subsubsection{P-value calculation}\label{p-value-calculation}}

Further, a visual test can involve \(K\) independent observers. Let
\(D_i = \{0,1\}\) be a binomial random variable denoting whether subject
\(i\) correctly detecting the actual data plot, and
\(X = \sum_{i=1}^{K}X_i\) be the number of observers correctly picking
the actual data plot. Then, by imposing a relatively strong assumption
on the visual test that all \(K\) evaluations are fully independent,
under the null hypothesis, \(X \sim \mathrm{Binom}_{K,1/m}\). Therefore,
the \(p\)-value of a lineup of size \(m\) evaluated by \(K\) observer is
given as \(P(X \geq x) = 1 - F(x) + f(x)\), where \(F(.)\) is the
cumulative distribution function, \(f(.)\) is the probability mass
function and \(x\) is the realization of number of observers correctly
picking the actual data plot \citep{majumder_validation_2013}.

As pointed out by \citet{vanderplas2021statistical}, the binomial model
doesn't take into account the possible dependencies in the visual test
due to repeated evaluations of the same lineup. And it is inapplicable
to visual test where subjects are asked to select one or more ``most
different'' plots from the lineup. They summarized three common
scenarios in visual inference: (1) \(K\) different lineups are shown to
\(K\) subjects, (2) \(K\) lineups with different null plots but the same
actual data plot are shown to \(K\) subjects, and (3) the same lineup is
shown to \(K\) subjects. Out of these three scenarios, Scenario 3 is the
most common in previous studies as it puts the least constraints on the
experimental design. For Scenario 3, \citet{vanderplas2021statistical}
modelled the probability of a plot \(i\) being selected from a lineup as
\(\theta_i\), where \(\theta_i \sim Dirichlet(\alpha)\) for
\(i=1,...,m\) and \(\alpha > 0\). And defined \(c_i\) to be the number
of times plot \(i\) being selected in \(K\) evaluations. In case subject
\(j\) makes multiple selections, they decided to add \(1/s_j\) to
\(c_i\) instead of one, where \(s_j\) is the number of plots subject
\(j\) selected for \(j=1,...K\). This ensured \(\sum_{i}c_i=K\). Thus,
the visual p-value followed by the above model is given as

@@

The parameter \(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial}
is usually unknown and hence needs to be estimated from the survey data.
For low values of \(\alpha\), only a few plots are attractive to the
observers and tend to be selected. For higher values of \(\alpha\), the
distribution of the probability of each plot being selected is more
evenly. \citet{vanderplas2021statistical} suggested that \(\alpha\) can
be estimated using maximum likelihood estimation or visual estimation.
But if \(\alpha\) is small and only a few null plots in a lineup are
attractive, MLE could fail to provide accurate estimates.

@@

\hypertarget{unknown}{%
\subsection{Unknown}\label{unknown}}

This should be a section that summarizes the background, gives the
motivation to the experiments, and most importantly reflects on the
title.
